---
title: "Thesis"
format:
  pdf:
    toc: true
    documentclass: scrartcl
    papersize: letter
    execute:
    echo: false
    warning: false
---

# Data

## Transparency international

### Perception Index data (2012-2023)

```{r}
library(openxlsx) 
library(writexl) 
library(haven) 
library(magrittr) 
library(readr) 
library(naniar) 
library(ggplot2) 
library(Hmisc) 
library(purrr) 
library(Rmisc)
library(data.table) 
library(dplyr) 
library(hrbrthemes) 
library(haven) 
library(gtExtras) 
library(kableExtra) 
library(gt) 
library(readxl) 
library(tidyverse)
library(scales)
```

```{r}
perception_data<-read_xlsx("./data/CPI2023_Global_Results__Trends.xlsx", sheet = 2)


```

```{r}

# Set the column names of df to the values in the 4th row
colnames(perception_data) <- as.character(perception_data[3, ])

# Remove the first 4 rows to delete everything above and including the original 4th row
perception_data <- perception_data[-(1:3), ]

```

## WJP

### Absence of corruption (2012-2023)

Factor 2

```{r}
absence_corrup_data<- read_xlsx("./data/2023_wjp_rule_of_law_index_HISTORICAL_DATA.xlsx", sheet = 12)

```

### Fundamental Rights (2012-2023)

Factor 4

```{r}
fundamental_rights_data<- read_xlsx("./data/2023_wjp_rule_of_law_index_HISTORICAL_DATA.xlsx", sheet = 12)
```

### Regulatory Enforcement (2012-2023)

Factor 6

```{r}
regulatory_enforcement_data<- read_xlsx("./data/2023_wjp_rule_of_law_index_HISTORICAL_DATA.xlsx", sheet = 12)
```

## United Nations

Office on Drugs and Crime (UNODC)

### Corruption: bribes and other types (2013-2021)

```{r}
corruption_UN<-read_xlsx("./data/data_cts_corruption_and_economic_crime (2).xlsx")

# Set the column names of df to the values in the 4th row
colnames(corruption_UN) <- as.character(corruption_UN[2, ])
corruption_UN <- corruption_UN[-(1:2), ]
```

### Bribery prevalence (2012-2021)

```{r}

bribery_prevalence<-read.csv("./data/bribery-prevalence-un.csv")
```

### GDP spend in Education (2000-2022)

```{r}
spend_education<-read.csv("./data/total-government-expenditure-on-education-gdp.csv")
```

### Human development Index

```{r}
human_index<-read.csv("./data/human-development-index.csv")

human_index_22<-read_xlsx('./data/HDR23-24_Statistical_Annex_HDI_Trends_Table.xlsx')

colnames(human_index_22) <- as.character(human_index_22[4, ])
human_index_22<- human_index_22[-(1:5), ]
```

## The Varieties of Democracy (V-Dem) project (2000-2022)

### Corruption in politics and more

```{r}
corruption_politics_data <- read_xlsx('./data/qogdata_05_03_2024.xlsx')


```

```{r}
corruption_v_dem<-read.csv("./data/V-Dem-CY-Full+Others-v14.csv")
```

### Judicial constrains in executive (2000-2022)

```{r}

judicial_executive<-read.csv("./data/judicial-constraints-on-the-executive-index.csv")

```

### **Other independent variables**

```{r}
other_v_dem<-read.csv("./data/V-Dem-CY-Full+Others-v14.csv")


```

## World Bank

### Economic growth

```{r}
eco_growth_data <- read_xls('./data/API_NY.GDP.MKTP.KD.ZG_DS2_en_excel_v2_27.xls')

colnames(eco_growth_data) <- as.character(eco_growth_data[3, ])
eco_growth_data <- eco_growth_data[-(1:3), ]


```

```{r}
gdp_percapita_data<- read_xls('./data/API_NY.GDP.PCAP.PP.CD_DS2_en_excel_v2_84017.xls')
colnames(gdp_percapita_data) <- as.character(gdp_percapita_data[3, ])
gdp_percapita_data<- gdp_percapita_data[-(1:3), ]

```

### Political Stability- no violence

Estimate of governance (ranges from approximately -2.5 (weak) to 2.5 (strong) governance performance). 2000-2022

```{r}
political_stabilty<- read_xlsx("./data/wgidataset.xlsx", sheet = 3)

colnames(political_stabilty) <- as.character(political_stabilty[13, ])
political_stabilty <- political_stabilty[-(1:13), ]
```

### Government Effectiveness

Estimate of governance (ranges from approximately -2.5 (weak) to 2.5 (strong) governance performance). 2000-2022

```{r}
government_effectiveness<- read_xlsx("./data/wgidataset.xlsx", sheet = 4)

colnames(government_effectiveness) <- as.character(government_effectiveness[13, ])
government_effectiveness <- government_effectiveness[-(1:13), ]
```

## Economist Intelligence Unit 

### Democracy Index (2006-2022)

```{r}

democracy_index<- read.csv("./data/democracy-index-eiu.csv")

```

# Clean corruption data

```{r}

# WJP absence corruption

corruption_1<- absence_corrup_data %>% 
  select(Country,Year, `Country Code`,`Factor 2: Absence of Corruption`, `2.1 Government officials in the executive branch do not use public office for private gain`,`2.2 Government officials in the judicial branch do not use public office for private gain`,`2.3 Government officials in the police and the military do not use public office for private gain`, `2.4 Government officials in the legislative branch do not use public office for private gain`)

#V_dem index 1
corruption_2<-corruption_politics_data %>% 
  select(cname,year,vdem_corr,ccodealp,bci_bci,ccp_cc,ti_cpi,vdem_mecorrpt,wbgi_cce,wdi_tacpsr)

#V_dem index 2
corruption_2_1<- corruption_v_dem %>% 
  select(country_name,country_text_id, year, v2jucorrdc,v2xnp_regcorr,v2x_corr,v2x_execorr,v2x_pubcorr,e_wbgi_cce, v2excrptps, v2exbribe, v2lgcrrpt, v2mecorrpt)

#UN
corruption_3<-corruption_UN %>% 
  select(Iso3_code,Country,Indicator,Dimension,Category,Year,VALUE, `Unit of measurement`)

#CPI Transparency
corruption_4<-perception_data %>% 
  select(`Country / Territory`,ISO3,`CPI score 2023`,`CPI score 2022`,`CPI score 2021`,`CPI score 2020`,`CPI score 2019`,`CPI score 2018`,`CPI score 2017`,`CPI score 2016`,`CPI score 2015`,`CPI score 2014`,`CPI Score 2013`,`CPI Score 2012`)

```

```{r}

#Change the names of the columns

#WJP
colnames(corruption_1) <- c('country','year','ISO','2_absence_corr','2.1_absence_corr', '2.2_absence_corr', '2.3_absence_corr', '2.4_absence_corr')

corruption_1$year<- ifelse(corruption_1$year == "2012-2013", 2013, ifelse(corruption_1$year == "2017-2018", 2018, corruption_1$year))



# Varieties democracy index

colnames(corruption_2)[1]<-('country')
colnames(corruption_2)[4]<-('ISO')

#Varieties democracy index_2_1

colnames(corruption_2_1)[1]<-('country')
colnames(corruption_2_1)[2]<-('ISO')

#UN
colnames(corruption_3)[1]<-('ISO')
colnames(corruption_3)[2]<-('country')
colnames(corruption_3)[6]<-('year')


corruption_3 <- corruption_3 %>% 
  filter(Category %in% c('Corruption', 'Corruption: Bribery', 'Corruption: Other acts of corruption'))


corruption_3 <- corruption_3 %>% 
  filter(`Unit of measurement`=='Rate per 100,000 population')



#Transparency International

colnames(corruption_4)[1]<-('country')
colnames(corruption_4)[2]<-('ISO')

```

```{r}
#Pivot data

# Pivot UN data

corruption_3_pivot<-corruption_3%>%
  pivot_wider(names_from = Category, values_from = VALUE)
colnames(corruption_3_pivot)[7]<-('un_corr')
colnames(corruption_3_pivot)[8]<-('un_corr_bribery')
colnames(corruption_3_pivot)[9]<-('un_corr_other')

#Pivot Transparency data
# Pivot the data to a long format
corruption_4_pivot<- corruption_4 %>% 
  pivot_longer(
    cols = starts_with("CPI"), # Select columns that start with "CPI_score"
    names_to = "year", # Name of the new column for the year
    values_to = "CPI_score", # Name of the new column for the CPI scores
    names_prefix = "CPI_score_" # Remove the prefix from the year column
  )
  
# Removing 'CPI score' from the 'year' column
corruption_4_pivot$year <- gsub("CPI score", "", corruption_4_pivot$year)
corruption_4_pivot$year <- gsub("CPI Score", "", corruption_4_pivot$year)

# Converting the 'year' column to numeric
corruption_4_pivot$year <- as.numeric(corruption_4_pivot$year)

# If there might be leading or trailing spaces after removing 'CPI score', you might want to trim those as well
corruption_4_pivot$year <- as.numeric(trimws(corruption_4_pivot$year))

```

```{r}
#YEARS
corruption_1_13_23<-corruption_1 %>% 
  filter(year>2011)

corruption_2_12_23<-corruption_2_1%>% 
   filter(year>2011)

corruption_3_13_21<-corruption_3_pivot %>% 
  filter(year>2011)

corruption_4_12_23<-corruption_4_pivot %>% 
  filter(year>2011)
```

## Available data and NAs in corruption data

```{r}
#NAs 
#corruption_1_13_23
na_counts_1 <- corruption_1_13_23 %>%
  group_by(country, year) %>%
  dplyr::summarise(across(everything(), ~sum(is.na(.))))

#corruption_2_12_23
na_counts_2 <- corruption_2_12_23 %>%
  group_by(country, year) %>%
  dplyr::summarise(across(everything(), ~sum(is.na(.))))

#corruption_3_13_21
na_counts_3 <- corruption_3_13_21 %>%
  group_by(country, year) %>%
  dplyr::summarise(across(everything(), ~sum(is.na(.))))

#corruption_4_12_23
na_counts_4 <- corruption_4_12_23 %>%
  group_by(country, year) %>%
  dplyr::summarise(across(everything(), ~sum(is.na(.))))
```

```{r}
countries_corr_1<-unique(corruption_1_13_23$ISO)
countries_corr_2<-unique(corruption_2_12_23$ISO)
countries_corr_3<-unique(corruption_3_13_21$ISO)
countries_corr_4<-unique(corruption_4_12_23$ISO)

```

```{r}
# Find intersection of ISO variable between the first two datasets
common_iso_1 <- intersect(corruption_1_13_23$ISO, corruption_2_12_23$ISO)

# 133 countries match
common_iso_2<- intersect(common_iso_1, corruption_4_12_23$ISO)

#82 countries in common
common_iso_3<-intersect(common_iso_2, corruption_3_13_21$ISO)
```

```{r}


#corr_merge<- merge(corruption_1_13_23, corruption_2_12_23, by=c('ISO', 'year'))

```

# Clean independent variables data

```{r}
other_v_dem_subdata<- other_v_dem %>% 
  select(country_name,country_text_id, year, v2x_polyarchy,
v2x_egaldem,
v2x_freexp_altinf,
v2x_cspart,
v2xeg_eqdr,
v2x_jucon,
v2xlg_legcon,
v2cltrnslw,
v2clacjust,
v2clacjstm,
v2clacjstw,
v2cldiscm,
v2cldiscw,
v2clacfree,
v2pepwrses,
v2pepwrsoc,
v2pepwrgen,
v2peedueq,
v2pehealth,
v2peapsecon,
v2peasbecon,
v2peasjgen,
v2cacamps,
v2x_accountability,
v2x_civlib,
v2x_clpol,
v2x_gender,
v2x_genpp,
v2x_rule,
v2smgovfilcap,
v2smregcap,
e_peaveduc,
e_peedgini,
e_gdp,
e_gdppc,
e_miinflat,
e_civil_war )
```

```{r}
all_v_dem_subdata<- other_v_dem %>% 
  select(country_name,country_text_id, year, v2x_polyarchy,
v2x_egaldem,
v2x_freexp_altinf,
v2x_cspart,
v2xeg_eqdr,
v2x_jucon,
v2xlg_legcon,
v2cltrnslw,
v2clacjust,
v2clacjstm,
v2clacjstw,
v2cldiscm,
v2cldiscw,
v2clacfree,
v2pepwrses,
v2pepwrsoc,
v2pepwrgen,
v2peedueq,
v2pehealth,
v2peapsecon,
v2peasbecon,
v2peasjgen,
v2cacamps,
v2x_accountability,
v2x_civlib,
v2x_clpol,
v2x_gender,
v2x_genpp,
v2x_rule,
v2smgovfilcap,
v2smregcap,
e_peaveduc,
e_peedgini,
e_gdp,
e_gdppc,
e_miinflat,
e_civil_war,
e_wbgi_cce,
v2jucorrdc,
v2x_corr,
v2mecorrpt,
v2xnp_regcorr,
v2x_execorr,
v2x_pubcorr,
v2exbribe,
v2excrptps,
v2lgcrrpt, v2cacamps,v2caviol,v2csreprss)



```

```{r}
#changing column names 
colnames(all_v_dem_subdata)[1]<-('country')
colnames(all_v_dem_subdata)[2]<-('ISO')
colnames(other_v_dem_subdata)[1]<-('country')
colnames(other_v_dem_subdata)[2]<-('ISO')
colnames(eco_growth_data)[1]<-('country')
colnames(eco_growth_data)[2]<-('ISO')

```

```{r}
#select only the imoortant columns 

eco_growth_data_clean<-eco_growth_data %>% 
  select(-`Indicator Code`)

# Pivot the data to a long format
eco_growth_data_clean_pivot<- eco_growth_data_clean %>% 
  pivot_longer(
    cols = 4:ncol(eco_growth_data_clean), 
    names_to = "year", 
    values_to = "gdp_growth"
  )

eco_growth_data_clean_pivot<-eco_growth_data_clean_pivot %>% 
  select(-`Indicator Name`)


```

```{r}
#YEARS

all_eco_growth_20_22<-eco_growth_data_clean_pivot %>% 
  filter(year>1999)

all_2_20_22<-all_v_dem_subdata %>% 
  filter(year>1999 & year<2023)

others_2_20_22<-other_v_dem_subdata%>% 
  filter(year>1999 & year<2023)



```

```{r}
# gdp per capita

#select only the imoortant columns 

gdp_data_clean<-gdp_percapita_data %>% 
  select(-`Indicator Code`)

# Pivot the data to a long format
gdp_data_clean_pivot<- gdp_data_clean %>% 
  pivot_longer(
    cols = 4:ncol(gdp_data_clean), 
    names_to = "year", 
    values_to = "gdp_percapita"
  )

gdp_data_clean_pivot<-gdp_data_clean_pivot %>% 
  select(-`Indicator Name`)

#YEARS

all_gdp_20_22<-gdp_data_clean_pivot %>% 
  filter(year>1999 & year<2023)

colnames(all_gdp_20_22)[1]<-('country')
colnames(all_gdp_20_22)[2]<-('ISO')

```

## Available data and NAs in independent data

```{r}
#all_2_12_23
na_counts_all_2 <- all_2_20_22%>%
  group_by(country, year) %>%
  dplyr::summarise(across(everything(), ~sum(is.na(.))))

#other_2_12_23
na_counts_other_2 <- others_2_20_22%>%
  group_by(country, year) %>%
  dplyr::summarise(across(everything(), ~sum(is.na(.))))



#gdp_2_20_22
na_all_eco_growth<-all_eco_growth_20_22 %>% 
  group_by(country, year) %>%
  dplyr::summarise(across(everything(), ~sum(is.na(.))))
```

```{r}
# Filter the dataframe to count only rows with 1 in the 'v2lgcrrpt' column
count_of_ones <- na_counts_all_2%>%
    dplyr::group_by(year, country) %>%
    dplyr::summarise(count = sum(v2lgcrrpt == 1, na.rm = TRUE))


```

```{r}
countries_with_ones <- na_counts_all_2 %>%
  dplyr::group_by(country) %>% # Assuming 'country' is the name of the country column
  dplyr::summarise(count = sum(v2lgcrrpt == 1, na.rm = TRUE)) %>%
  dplyr::filter(count >= 1)

```

```{r}
# Check for NAs in each row, excluding the first three columns
na_check <- apply(all_2_20_22[, -c(1, 2, 3)], 1, function(x) any(is.na(x)))

# Subset the original dataframe to include only rows with any NA values in the variables
na_rows <- all_2_20_22[na_check, ]

# Create a summary dataframe
na_summary <- na_rows[, c("country", "year")]


na_detail <- apply(all_2_20_22[, -c(1, 2, 3)], 1, function(x) {
  if(any(is.na(x))) {
    paste(names(which(is.na(x))), collapse=", ")
  } else {
    NA
  }
})

na_summary$na_columns <- na_detail[na_check]


```

# Data without NAs

```{r}
clean_all_2_20_22<- all_2_20_22 %>% 
  select(country, ISO, year, v2x_polyarchy,
v2x_egaldem,
v2x_freexp_altinf,
v2x_cspart,
v2xeg_eqdr,
v2x_jucon,
v2cltrnslw,
v2clacjust,
v2clacjstm,
v2clacjstw,
v2cldiscm,
v2cldiscw,
v2clacfree,
v2pepwrses,
v2pepwrsoc,
v2pepwrgen,
v2peedueq,
v2pehealth,
v2x_accountability,
v2x_civlib,
v2x_clpol,
v2x_rule,
v2smgovfilcap,
v2smregcap,
v2jucorrdc,
v2x_corr,
v2mecorrpt,
v2xnp_regcorr,
v2x_execorr,
v2x_pubcorr,
v2exbribe,
v2excrptps)


#option 2

clean_2_all_2_20_22<- all_2_20_22 %>% 
  select(country, ISO, year, v2x_polyarchy,
v2x_egaldem,
v2x_freexp_altinf,
v2x_cspart,
v2xeg_eqdr,
v2x_jucon,
v2cltrnslw,
v2clacjust,
v2clacjstm,
v2clacjstw,
v2cldiscm,
v2cldiscw,
v2clacfree,
v2pepwrses,
v2pepwrsoc,
v2pepwrgen,
v2peedueq,
v2pehealth,
v2x_accountability,
v2x_civlib,
v2x_clpol,
v2x_rule,
v2smgovfilcap,
v2smregcap,
v2jucorrdc,
v2x_corr,
v2mecorrpt,
v2xnp_regcorr,
v2x_execorr,
v2x_pubcorr,
v2exbribe,
v2excrptps,
v2lgcrrpt,v2cacamps,v2caviol,v2csreprss)


clean_all_2_20_22<- clean_all_2_20_22%>% 
  filter(ISO!='TLS')

clean_all_2_20_22<- clean_all_2_20_22%>% 
  filter(ISO!='BHR')


na_counts_all_clean_vdem <- clean_all_2_20_22%>%
  group_by(country, year) %>%
  dplyr::summarise(across(everything(), ~sum(is.na(.))))
```

```{r}
# First, find the ISO codes of countries with at least one NA in gdp_growth
iso_with_na <- all_eco_growth_20_22%>% 
  group_by(ISO) %>% 
  filter(any(is.na(gdp_growth))) %>% 
  dplyr::summarise() 
  

# Then, filter out the rows with those ISO codes
clean_growth_20_22<- all_eco_growth_20_22 %>% 
  filter(!(ISO %in% iso_with_na$ISO))
```

```{r}


# Identify ISO codes with at least one NA in any column
iso_with_na_2 <- clean_all_2_20_22 %>% 
  group_by(ISO) %>% 
  filter(any(is.na(.))) %>%
  dplyr::summarise(na_row_count = n())
```

```{r}
# gdp per capita
# First, find the ISO codes of countries with at least one NA in gdp_growth
gdp_iso_with_na <- all_gdp_20_22%>% 
  group_by(ISO) %>% 
  filter(any(is.na(gdp_percapita))) %>% 
  dplyr::summarise() 
  

# Then, filter out the rows with those ISO codes
clean_gdp_20_22<- all_gdp_20_22 %>% 
  filter(!(ISO %in% gdp_iso_with_na$ISO))

# Identify ISO codes with at least one NA in any column
iso_gdp_with_na_2 <- clean_gdp_20_22%>% 
  group_by(ISO) %>% 
  filter(any(is.na(.))) %>%
  dplyr::summarise(na_row_count = n())

```

```{r}
merged_data<- merge(clean_all_2_20_22,clean_growth_20_22, by=c('year','ISO'))

merged_data<-merged_data %>% 
  select(-country.y)

colnames(merged_data)[3]<-('country')




```

# Normalize data

Without the WB data

```{r}
nor_all_2_20_22 <- clean_all_2_20_22
columns_to_scale <- names(nor_all_2_20_22)[4:ncol(nor_all_2_20_22)]

# Applying the Min-Max scaling
nor_all_2_20_22[columns_to_scale] <- lapply(nor_all_2_20_22[columns_to_scale], function(x) {
  rescale(x, to = c(0, 1), from = range(x, na.rm = TRUE))
})



```

```{r}
#Change the direction of the corruption index so the countries with the less corruption have the highest values

nor_all_2_20_22$v2x_corr_2 <- 1 - nor_all_2_20_22$v2x_corr
```

```{r}
#save dataset 1

#write.csv(nor_all_2_20_22, "./data/clean_data_1.csv", row.names = FALSE)


```

With the WB data

```{r}
merged_data$gdp_growth <- as.numeric(merged_data$gdp_growth)

wb_all_2_20_22 <- merged_data
columns_to_scale <- names(wb_all_2_20_22)[4:ncol(wb_all_2_20_22)]



# Applying the Min-Max scaling
wb_all_2_20_22[columns_to_scale] <- lapply(wb_all_2_20_22[columns_to_scale], function(x) {
  rescale(x, to = c(0, 1), from = range(x, na.rm = TRUE))
})


```

```{r}


wb_all_2_20_22$v2x_corr_2 <- 1 - wb_all_2_20_22$v2x_corr

unique<-unique(wb_all_2_20_22$ISO)
```

```{r}
#save dataset 2

#write.csv(wb_all_2_20_22, "./data/clean_data_2.csv", row.names = FALSE)
```

```{r}
# Create a data frame of all possible combinations of ISO codes and years
all_iso <- unique(wb_all_2_20_22$ISO)
all_years <- 2000:2022
complete_set <- expand.grid(ISO = all_iso, year = all_years)

# Check for missing combinations in the original dataset
missing_combinations <- anti_join(complete_set, wb_all_2_20_22, by = c("ISO", "year"))

# View missing combinations
if(nrow(missing_combinations) > 0) {
  print(missing_combinations)
} else {
  print("All ISO-year combinations are present.")
}
```

# Data that includes gdp growth

```{r}
clean_2_all_2_20_22<- clean_2_all_2_20_22%>% 
  filter(ISO!='TLS')

clean_2_all_2_20_22<- clean_2_all_2_20_22%>% 
  filter(ISO!='BHR')


na_2_counts_all_clean_vdem <- clean_2_all_2_20_22%>%
  group_by(country, year) %>%
  dplyr::summarise(across(everything(), ~sum(is.na(.))))
```

```{r}
clean_legis<- clean_2_all_2_20_22 %>%
  drop_na()
 
```

```{r}
available_years_by_country <- clean_legis %>%
  group_by(ISO) %>%
  dplyr::summarise(years = list(year))
```

```{r}
# Define the range of desired years
desired_years <- 2000:2022

# Create a new dataframe with only countries having complete data from 2000 to 2022
complete_data_countries <-clean_legis %>%
  group_by(country) %>%
  # Check if all desired years are present for each country
  filter(all(desired_years %in% year)) %>%
  ungroup()  # Ungroup to remove the grouping

unique(complete_data_countries$ISO)
```

```{r}
# First, find the ISO codes of countries with at least one NA in gdp_growth
iso_with_na <- all_eco_growth_20_22%>% 
  group_by(ISO) %>% 
  filter(any(is.na(gdp_growth))) %>% 
  dplyr::summarise() 
  

# Then, filter out the rows with those ISO codes
clean_growth_20_22<- all_eco_growth_20_22 %>% 
  filter(!(ISO %in% iso_with_na$ISO))

#unique(clean_growth_20_22$ISO)
```

```{r}
merged_data_2<- merge(complete_data_countries,clean_growth_20_22, by=c('ISO','year'))

merged_data_2<-merged_data_2 %>% 
  select(-country.y)

colnames(merged_data_2)[3]<-('country')

m2<-unique(merged_data_2$ISO)
```

```{r}
merged_data_2$gdp_growth <- as.numeric(merged_data_2$gdp_growth)

wb_2_all_2_20_22 <- merged_data_2
columns_to_scale <- names(wb_2_all_2_20_22)[4:ncol(wb_2_all_2_20_22)]



# Applying the Min-Max scaling
wb_2_all_2_20_22[columns_to_scale] <- lapply(wb_2_all_2_20_22[columns_to_scale], function(x) {
  rescale(x, to = c(0, 1), from = range(x, na.rm = TRUE))
})

```

```{r}

wb_2_all_2_20_22$v2x_corr_2 <- 1 - wb_2_all_2_20_22$v2x_corr
wb_2_all_2_20_22$v2x_execorr_2 <- 1 - wb_2_all_2_20_22$v2x_execorr
#wb_2_all_2_20_22$v2jucorrdc_2 <- 1 - wb_2_all_2_20_22$v2jucorrdc
#wb_2_all_2_20_22$v2lgcrrpt_2 <- 1 - wb_2_all_2_20_22$v2lgcrrpt
wb_2_all_2_20_22$v2cacamps_2 <- 1 - wb_2_all_2_20_22$v2cacamps
wb_2_all_2_20_22$v2caviol_2 <- 1 - wb_2_all_2_20_22$v2caviol
unique<-unique(wb_2_all_2_20_22$ISO)
```

```{r}
#write.csv(wb_2_all_2_20_22, "./data/clean_data_3.csv", row.names = FALSE)
```

# Data that includes gdp growth and gdp per capita)

```{r}
merged_data_3<- merge(wb_2_all_2_20_22,clean_gdp_20_22, by=c('ISO','year'))
merged_data_3<-merged_data_3 %>% 
  select(-country.y)

colnames(merged_data_3)[3]<-('country')

m3<-unique(merged_data_3$ISO)
```

```{r}

merged_data_3$gdp_percapita <- as.numeric(merged_data_3$gdp_percapita)

wb_3_all_2_20_22 <- merged_data_3
#columns_to_scale <- names(wb_3_all_2_20_22)[39:ncol(wb_3_all_2_20_22)]



# Applying the Min-Max scaling
#wb_3_all_2_20_22[columns_to_scale] <- lapply(wb_3_all_2_20_22[columns_to_scale], function(x) {
  #rescale(x, to = c(0, 1), from = range(x, na.rm = TRUE))
#})
```

```{r}
#write.csv(wb_3_all_2_20_22, "./data/clean_data_4.csv", row.names = FALSE)
```
